The \frb\ Campaign: Multi-Observatory Radio Burst and Implications for the FRB Population

### 2017-03-10 repeater-vladata.tex
fixed label on timeline figure

\author{P.~Scott}
\affiliation{University of Cambridge, UK}

@@

\author{D.~Titterington}
\affiliation{University of Cambridge, UK}

@@

@@

To study how the input parameters affect the measured flux distribution, so we generated 100 populations to measure 68\% confidence intervals on the cumulative flux distribution index. Figure \ref{fig:ind} shows the result of several such measurements for input luminosity distribution index ranging from --2.2 to --1.2. Generally, the measured flux distribution index flattens as the input luminosity distributions flattens. The best constraint on the flux distribution index \citep{2016ApJ...830...75V} requires an input energy distribution index between roughly --2.1 and --1.4, which is consistent with the measured energy distribution for \frb. These simulations predict a mean a mean redshift between 0.9 and 1.8, which is in weak tension with the mean FRB redshift inferred from DM. For a mean total DM of $750$\ pc cm$^{-3}$ and a mean host DM of 200 pc cm$^{-3}$, we expect a mean redshift of $\sim0.5$ \citep{2004MNRAS.348..999I}.

>>>>

\author{P.~Scott}
\affiliation{Astrophysics Group, Cavendish Laboratory, 19 J. J. Thomson Avenue, Cambridge CB3 0HE, UK}

@@

\author{D.~Titterington}
\affiliation{Astrophysics Group, Cavendish Laboratory, 19 J. J. Thomson Avenue, Cambridge CB3 0HE, UK}

@@

**Burst temporal width**

**Corner plot?**

@@

To study how the input parameters affect the measured flux distribution, so we generated 100 populations to measure 68\% confidence intervals on the cumulative flux distribution index. Figure \ref{fig:ind} shows the result of several such measurements for input luminosity distribution index ranging from --2.2 to --1.2. Generally, the measured flux distribution index flattens as the input luminosity distributions flattens. The best constraint on the flux distribution index \citep{2016ApJ...830...75V} requires an input energy distribution index between roughly --2.1 and --1.4, which is consistent with the measured energy distribution for \frb. These simulations predict a mean a mean redshift between 0.9 and 1.8, which is in weak tension with the mean FRB redshift inferred from DM. For a mean total DM of $750$\ pc cm$^{-3}$ and a mean host DM of 200 pc cm$^{-3}$, we expect a mean redshift of $\sim0.6$ \citep[$z=DM/900$\ pc cm$^{-3}$;][]{2004MNRAS.348..999I}.
